### 2019-03-09 manuscript/introduction.tex
tex typos

%B: the key alteration below is an attempt at easing the transitions of the complicated existing logical structure, which intermixes advances with setbacks and problems.
%B: the "Here, we" part should maybe come at the bottom of introduction, and it's a little early for here, in the first paragraph.
Species accumulate around the tree of life at different rates.
A possible explanation for this phenomenon is that species possess traits that cause unequal rates of diversification. %B: new.
The search for influential traits has been accelerated by a dramatic increases in data and an advance in methods, which now make use of far more information from phylogenetic trees \citep{maddison_2007}. 
Despite some setbacks \citep{maddison_2015, rabosky_2015, moore_2016}, advances in analytical methods \citep{fitzjohn_2009, goldberg_2012, beaulieu_2016, rabosky_2017} are enabling the discovery of traits that alter the diversification patterns. %B: the following is now orphaned, because it's inclusion merits addition of non-trait-focused methods; "potentially interesting biological processes"
Nevertheless, the aim of identifying the focal trait and investigating its association with rates of speciation and extinction remains complicated. 
This is, in part, because the context in which traits occur can lead to complex interactions with the diversification process (see \citet{caetano_2018, herrera_2018}). 
Trait combinations provide examples of such context, and may be of particular interest, given the rapid accumulation of information about traits. %cite?
Two exceedingly well-studied traits, ploidy and breeding system, are of particular interest. 
Their individual state-dependent contributions to the process of diversification, as well as influence on each others' trait transitions, have long been the focus of speculation and study \citep{stebbins1950}.

%B: IMO: ploidy = trait, di-, tri-, tetra-, hexa-, etc. (including "poly-") = trait states; the uncertainty we were discussing is whether "tri-" < "poly-" or "tri-" = "poly-"
%(sorry about the confusion: I accidentally mis-wrote in the commented-out banter with %E.)
% was [B&E banter] and % R- I think the trait is polyploidy and the state is ploidy (as 2, or +2). I will go with everyone else in the literature and use polyploidy
Whole genome duplication is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
Such changes is ploidy have the potential to affect many other phenotypes, and therefore alter a variety of evolutionary \citep{ramsey_2002} and ecological processes \citep{sessa_2019}.
The prevalence of ploidy variation has been broadly considered as a salient feature of flowering plants for nearly a century \citep{stebbins1938}. 
Polyploids have long been thought to have lower (and even negative) rates of net diversification than diploids \citet{mayrose_2011, mayrose_2015}. 
A number of recent studies, however, find common paleo-polyploidization, including at the base of many highly diverse angiosperm clades \citep{soltis_2014}. 
%B: explanation for this edit, rm: "Using the genomic evidence  from the 1KP project" : this is the data, not the approach; Ks and tree reconciliation are particularly troubling and weak modes of inference. I am okay with having this point to what others have found, but I would prefer to avoid endorsing what I see as a deeply problematic set of methods.
\citet{landis_2018}, for example, found 106 whole genome duplications within angiosperms that, combined with a state-dependent diversification model, resulted in approximately 60\% of whole genome duplication events potentially enhancing net diversification.
The mere occurrence of such ancestral whole genome duplications points to an possibly important role of genome downsizing and diploidization in the diversification process \citep{soltis_2015diploidization, dodsworth_2015}. 
The presence of a significant and positive net diversification rate for (some) diploids can be  the result of a polyploid lineage that has been diploidized. 
Under this scenario, rather than being a macroevolutionary dead-end, polyploidy may instead be positively associated with the diversification process.

Ploidy has long been thought to affect the propensity for self-fertilization \citep{stebbins1950}. 
The evidence for correlated shifts in mating system, from outcrossing to selfing, after polyploidization appears limited and sometimes contradictory \citep{barringer2007, barrett2008, husband2008}.
In other cases, however, polyploidy is not only suspected to correlate with breeding system but causes the transition from self-incompatibility (SI) to self-compatibility(SC) \citep{stout1942, lewis1947}.
Doubled number of alleles in pollen is thought to effect disruption of the genetic mechanisms in gametophytic SI systems, which prevent self-fertilization \citep{entani1999, tsukamoto2005, kubo2010}. 
This creates a correlation between polyploidy and SC by precluding the existence of SI polyploids.
In clades with these systems, it is thus natural to consider the simultaneous macroevolution of polyploidy and breeding system.

>>>>

%B: the key alteration below is an attempt at easing the transitions of the complicated existing logical structure, which intermixes advances with setbacks and problems.
%B: the "Here, we" part should maybe come at the bottom of introduction, and it's a little early for here, in the first paragraph.
Species accumulate around the tree of life at different rates.
A possible explanation for this phenomenon is that species possess traits that cause unequal rates of diversification. %B: new.
The search for influential traits has been accelerated by a dramatic increases in data and an advance in methods, which now make use of far more information from phylogenetic trees \citep{maddison_2007}. 
Despite some setbacks \citep{maddison_2015, rabosky_2015, moore_2016}, advances in analytical methods \citep{fitzjohn_2009, goldberg_2012, beaulieu_2016, rabosky_2017} are enabling the discovery of traits that alter the diversification patterns. %B: the following is now orphaned, because it's inclusion merits addition of non-trait-focused methods; "potentially interesting biological processes"
Nevertheless, the aim of identifying the focal trait and investigating its association with rates of speciation and extinction remains complicated. 
This is, in part, because the context in which traits occur can lead to complex interactions with the diversification process \citep[see][]{caetano_2018, herrera_2018}.
Trait combinations provide examples of such context, and may be of particular interest, given the rapid accumulation of information about traits. %cite?
Two exceedingly well-studied traits, ploidy and breeding system, are of particular interest. 
Their individual state-dependent contributions to the process of diversification, as well as influence on each others' trait transitions, have long been the focus of speculation and study \citep{stebbins1950}.

%B: IMO: ploidy = trait, di-, tri-, tetra-, hexa-, etc. (including "poly-") = trait states; the uncertainty we were discussing is whether "tri-" < "poly-" or "tri-" = "poly-"
%(sorry about the confusion: I accidentally mis-wrote in the commented-out banter with %E.)
% was [B&E banter] and % R- I think the trait is polyploidy and the state is ploidy (as 2, or +2). I will go with everyone else in the literature and use polyploidy
Whole genome duplication is a remarkably common mutation in plants \citep{husband_2013, zenilferguson_2017}.
Such changes is ploidy have the potential to affect many other phenotypes, and therefore alter a variety of evolutionary \citep{ramsey_2002} and ecological processes \citep{sessa_2019}.
The prevalence of ploidy variation has been broadly considered as a salient feature of flowering plants for nearly a century \citep{stebbins1938}. 
Polyploids have long been thought to have lower (and even negative) rates of net diversification than diploids \citep{mayrose_2011, mayrose_2015}. 
A number of recent studies, however, find common paleo-polyploidization, including at the base of many highly diverse angiosperm clades \citep{soltis_2014}. 
%B: explanation for this edit, rm: "Using the genomic evidence  from the 1KP project" : this is the data, not the approach; Ks and tree reconciliation are particularly troubling and weak modes of inference. I am okay with having this point to what others have found, but I would prefer to avoid endorsing what I see as a deeply problematic set of methods.
\citet{landis_2018}, for example, found 106 whole genome duplications within angiosperms that, combined with a state-dependent diversification model, resulted in approximately 60\% of whole genome duplication events potentially enhancing net diversification.
The mere occurrence of such ancestral whole genome duplications points to an possibly important role of genome downsizing and diploidization in the diversification process \citep{soltis_2015diploidization, dodsworth_2015}. 
The presence of a significant and positive net diversification rate for (some) diploids can be  the result of a polyploid lineage that has been diploidized. 
Under this scenario, rather than being a macroevolutionary dead-end, polyploidy may instead be positively associated with the diversification process.

Ploidy has long been thought to affect the propensity for self-fertilization \citep{stebbins1950}. 
The evidence for correlated shifts in mating system, from outcrossing to selfing, after polyploidization appears limited and sometimes contradictory \citep{barringer2007, barrett2008, husband2008}.
In other cases, however, polyploidy is not only suspected to correlate with breeding system but causes the transition from self-incompatibility (SI) to self-compatibility (SC) \citep{stout1942, lewis1947}.
Doubled number of alleles in pollen is thought to effect disruption of the genetic mechanisms in gametophytic SI systems, which prevent self-fertilization \citep{entani1999, tsukamoto2005, kubo2010}. 
This creates a correlation between polyploidy and SC by precluding the existence of SI polyploids.
In clades with these systems, it is thus natural to consider the simultaneous macroevolution of polyploidy and breeding system.
